### 2023-02-01 files/Chapter7/Beam.tex
2d beam validity started

\documentclass[../../main.tex]{subfiles}
\begin{document}
\section{Validity of the Timoshenko beam model}
This section is a literature study of the article \cite{LVV09}. The goal of \cite{LVV09} to show that the one-dimensional Timoshenko beam theory, is a feasible model to use in practical applications of beams. In the real world, a beam is a complex three-dimensional model. Therefore it is important to validate the accuracy of a simlified theory like the Timoshenko beam theory for practical applications.\\

In mathematical terms, the validity of the Timoshenko beam theory is described as how well the solutions of the Timoshenko beam theory compare to more realistic, higher-dimensional models. It is obvious that a three-dimensional beam model is a better approximation of a real world beam. But the Timoshenko beam theory is less complex and more widely used.\\

The authors of \cite{LVV09} use a two-dimensional cantilever beam, to validate the use of a cantilever Timoshenko beam for practical importance. Although a direct comparison to a three-dimensional beam would be preferred, the authors state that this would introduce complexities. A two-dimensional model is therefore used as an intermediate step.\\

Where \cite{LVV09} differs from most other research, is that the boundary conditions are also taken into consideration.\\

@@

\subsection{The models}
Recall the cantilever Timoshenko beam model from section \ref{ssec:1D_Model:ModelProblems}, referred to as Problem T-2 and the cantilever two-dimensional beam model from section \ref{ssec:2D_Model:ModelProblem}, referred to as Problem 2D-1. In \cite{LVV09} it is assumed that the beams have a rectangular cross-section.\\

@@

In Chapter 1, the following parameters were established. The parameter $h$ is the height of the two-dimensional beam and for the Timoshenko dimensionless constant $\displaystyle \alpha = \frac{A \ell^2}{I}$ was found.\\

@@

\section{Validity of the two-dimensional elastic model}
In this section, the validity of a two-dimensional cantilever beam is investigated. This is a natural extension of the work in \cite{LVV09}. The authors mentioned this.\\

The model that will be considered is the two-dimensional elastic body defined in Chapter 1. The investigation will focus on the results relating to beam type problems.

and eigenfunctions of the models to determine the validity of the two-dimensional model. This investigation remains focussed on beam type problems.

@@

For both models the parameter $h$ represents the width of the beams. The three-dimensional model also have depth $b$. Intuitively, the two-dimensional beam should compare well the the three-dimensional beam if $b$ is small.

>>>>

\documentclass[../../main.tex]{subfiles}
\begin{document}
\section{Validity of the Timoshenko beam model}
This section is a literature study of the article \cite{LVV09}. The goal of \cite{LVV09} to show that the one-dimensional Timoshenko beam theory, is a feasible model to use in practical applications of beams. In the real world, a beam is a complex three-dimensional model. So a three-dimensional model would be a good approximation and better than a one-dimensional model. It is therefore important to validate the accuracy of a simlified theory like the Timoshenko beam theory.\\

In the article, the authors validate the Timoshenko beam theory by comparing it to a more realistic, two-dimensional model. The authors use a cantilever beam as a model. Although a direct comparison to a three-dimensional beam would be preferred, the authors state that this would introduce complexities. The two-dimensional model is an intermediate step.\\

Where \cite{LVV09} differs from most other research into the validity of the Timoshenko beam theory, is that the boundary conditions are also taken into consideration.\\

@@

\subsection{The models}
In the article, the authors use a cantilever configuration for the two models. Therefore the models presented here are also cantilever models.\\

Recall the cantilever Timoshenko beam model from section \ref{ssec:1D_Model:ModelProblems}, referred to as Problem T-2 and the cantilever two-dimensional beam model from section \ref{ssec:2D_Model:ModelProblem}, referred to as Problem 2D-1. In \cite{LVV09} it is assumed that the beams have a rectangular cross-section.\\

@@

In Chapter 1, the following parameters were defined. The parameter $h$ is the height of the two-dimensional beam and for the Timoshenko dimensionless constant $\displaystyle \alpha = \frac{A \ell^2}{I}$ was found.\\

@@

\section{Validity of the two-dimensional elastic model}
In this section, the validity of a two-dimensional cantilever beam is investigated. This is a natural extension of the work in \cite{LVV09}. This was mentioned by the authors.\\

As mentioned before, the two-dimensional model is used as a intermediate step between the Timoshenko and three-dimensional beam. The same method as in \cite{LVV09} will be used to investigate the validity of the two-dimensional model.\\

The models for the two-dimensional and three-dimensional beams are defined in section \ref{ssec:2D_Model:ModelProblem} and \ref{ssec:3D_Model:ModelProblems} respectively. These models are elastic bodies and not specifically beam models. Therefore it is expected to find eigenvalue and eigenfunction pairs that does not relate to beam type problems. This was already seen with the two-dimensional model in the previous section. These not beam type eigenvalues are calculated in this section, however the focus still remains on beam type problems.\\

@@

For both models the parameter $h$ represents the width of the beams. The three-dimensional model also have depth $b$. Intuitively, from the figure, the two-dimensional beam should compare better to the three-dimensional beam for smaller $b$.
